---
title: "D3 Bar Graph V2"
author: "Nathan Frey"
date: "February 18, 2016"
output: html_document
---

This is my attempt to make a bar graph using R and D3 keeping all the D3 stuff inside of the HTMLWidgets.widget function. I'm using GitHub only as an online backup. This is simply a testing ground. 

```{r}
library(htmlwidgets)
library(roxygen2)
library(devtools)
library(jsonlite)
library(networkD3) #For examples and MisLinks and MisNodes data

```
A quick function to examine data:  
```{r}
lu<- function(x){length(unique(x))}

```
Get the data:
```{r}
set.seed(123)
numz<- round(runif(15, min=3, max=20),0)
numz
```

Now, we'll set up the file scaffolding. I need to find out if running these after I have done work on the widget JavaScript code and R code will wipe out my work. I'll just run this onceInstead, only run the devtools::install() to rebuild the widget and launch it.  
```{r}

#create("d3BarGraphV2") #create the package skelton
#htmlwidgets::scaffoldWidget("d3BarGraphV2") 
```

Now make the necessary edits to the .yaml file, pyramid.R file, and pyramid.js files.   

I edited the yaml file, added the D3 library as a dependecy, and then told it to use the style.css as the stylesheet. I am not sure if this is correct, but I am going to give it a try.

The next steps are to build the package, as per Hilary Parker's guide...  
```{r}
getwd()


#If needed for testing:
setwd("/Users/Nathan/Dropbox/R Projects Personal/d3BarGraphV2")

document() #create the man folder, automatically generate the pyramid.Rd file
```

Now to install and run the package! Hopefully it works (Fingers crossed)  

```{r}
getwd()
setwd("..")
getwd()
install("d3BarGraphV2")
```

Let's load the library and make a go at it!

```{r}
library(d3BarGraphV2)
d3BarGraphV2::d3BarGraphV2(numz, width = 300, height = 300) #somehow fails. How do I find out why/where?

```


For quickly rebuilding and attempting to launch:  
```{r}
#Making function
redoD3<- function(){
setwd("/Users/Nathan/Dropbox/R Projects Personal/d3BarGraphV2")
document() #create the man folder, automatically generate the pyramid.Rd file
setwd("..")
install("d3BarGraphV2")
library(d3BarGraphV2)
} #End  redoD3 Function

# Usage
redoD3()




relaunchD3<- function(){
  redoD3()
  d3BarGraphV2::d3BarGraphV2(numz, width = 500, height = 500)
  
}
relaunchD3()

rebaseD3<- function(){
  redoD3()
  d3BarGraphV2::d3BarGraphV2(numz)
  }
rebaseD3()


#d3BarGraph::d3BarGraph(numz, width = 300, height = 300) #somehow fails. not sure ATM...

# Working, from Juba: 
d3BarGraphV2(c(1,5,10,6))
d3BarGraphV2(sample(1:20, 50, replace=TRUE))

d3BarGraphV2::d3BarGraphV2(numz, width = 500, height = 500)

#set.seed(123)
# numz<- round(runif(15, min=3, max=20),0) #15 whole numbers between 3 and 20
makeJSON<- function(numz) {
tst<- noquote(paste(numz, collapse = ","))
tstjson<- noquote(paste0("[", tst, "];"))
return(tstjson)
}
makeJSON(numz) #[1] [8,16,10,18,19,4,12,18,12,11,19,11,15,13,5];


```


































































































